The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-08-19 method.tex
start to structure the paper
tell the philosophy

\subsubsection{Platform agent} % (fold)
\label{ssub:platform_agent}
matching the 
% subsubsection platform_agent (end)

@@

>>>>

\subsubsection{Platform agent} % (fold)
\label{ssub:platform_agent}
matching the 
\begin{figure}

\begin{tikzpicture}
\begin{class}[text width=8cm]{Job}{0,0}
    \attribute{needCapacity : Map}
    \operation{lala(haha): void}
\end{class}
\end{tikzpicture}
\caption{Test UML Diagram}

\end{figure}
% subsubsection platform_agent (end)

@@

\subsubsection{Design philosopher} % (fold)
\label{ssub:design_philosopher}
platform create demander and provider
demander, a subclass of user, generate need i.e. create order (the defined task bunch)
    task is a subclass of job, need to be processed with specified resource type and amount(type,amount) , have its process time.
provider, a subclass of user, provider resource with different type and capacity, these resources can be allocated to task job and service-call job, service-call is subclass of job, which is the job to combined to create service.

the two type of job, task and service call, have something in common that need to be processd with resource. for task, the resource is renewable, for service-call, the resource is unrenewable.

service can be generated after the finish of service-call, so it belongs to the user who generate the service-call. service more like a contract

service-call come out driven by the task need, when a task appears frequently, provider proposed the job that have the same configuration. so the service generated by the service-call will suit for the specificed task.

good for service: efficieny, do not have to coordinated anymore, flexibe wile process with task, with the outsource trick, slice the taks, co-worked by all the useful resources.
bad for service: task-oriented, can only process specified task,

% subsubsection design_philosopher (end)

\subsubsection{Main functions} % (fold)
\label{ssub:main_functions}
service - task outsource
% subsubsection main_functions (end)

\subsubsection{Main problem} % (fold)
\label{ssub:main_problem}

% subsubsection main_problem (end)

\subsubsection{Main flow design} % (fold)
\label{ssub:main_flow_design}
\begin{itemize}
    \item generate provider and demander
    \item generate order (with task)
    \item generate resources
    \item process tasks (with only resource)
    \item organize service
    \item process task (plus service)
    \item Review and elimination of provider and service
\end{itemize}
% subsubsection main_flow_design (end)
